ESRC SDAI Application

### 2019-06-19 case_for_support.tex
Anna update

\textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In this research project, we will be using the CSEW and WMP datasets to investigate some of the environmental predictors of domestic abuse. First, using data from the CSEW, we will be looking at the association between neighbourhood-level characteristics, and the prevalence of domestic abuse as well the decision to report, and we will complement this with an additional analysis on WMP and census data. Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these. Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns. Second, we will be looking at how time-varying factors affect domestic abuse.

@@

@@

\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant association between the prevalence of domestic abuse, and the willingness to report and the environmental characteristics of the neighbourhood they live in. Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection to the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse. Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics of the area to predict the number of reported abuse cases. \textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level}.

>>>>

\textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In this research project, we will be using the CSEW and WMP datasets, as well as external sources of data to investigate some of the environmental predictors of domestic abuse. First, using data from the CSEW and drawing on previous research on the topic, we will be looking at the association between neighbourhood-level characteristics, and the prevalence of domestic abuse as well the decision to report. We will complement this with an additional analysis on WMP and census data. We will be able to account for the dynamic nature of these neighbourhood characteristics, by using longitudinal and repeated cross-sectional datasets. Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.

Second, we will be looking at how time-varying factors affect domestic abuse.

@@

\href{https://journals.sagepub.com/doi/abs/10.1177/1524838012445641?journalCode=tvaa}{
The Impact of Neighborhoods on Intimate Partner Violence and Victimization
}

the type sof social tie matters: friendship ties reduce the risk of IPV, family ties have no effect

@@

\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant associations between the prevalence of domestic abuse, the willingness to report, and the environmental characteristics of the neighbourhood they live in. Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these. For example, social disorganization theory posits that neighbourhood disadvantage is associated with an increased risk of domestic abuse.

Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection to the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse. Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics of the area to predict the number of reported abuse cases. \textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level}.
